RIT Department of Computer Science\\MSc Thesis Pre-Proposal:\\\emph{Design and Implementation of a Push-Based Signal-Function FRP System}

### 2011-08-30 Docs/Preproposal/preproposal.tex
proposed final draft of preproposal

\documentclass[11pt]{artikel3}
\usepackage{fullpage, setspace, graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{url}

\title{RIT Department of Computer Science\\MSc Thesis Pre-Proposal:\\\emph{Implementation of a Push-Based Signal-Function FRP System and Evaluation Interface}}
\author{Edward Amsden}
\date{\today}

@@

I intend to show that a monadic evaluation interface and signal vector typing enable a useful push-based FRP system.

@@

>>>>

\documentclass[11pt]{artikel3}
\usepackage{fullpage, setspace, graphicx}
\usepackage[margin=.75in]{geometry}
\usepackage{times}
\usepackage{url}

\title{RIT Department of Computer Science\\MSc Thesis Pre-Proposal:\\\emph{Design and Implementation of a Push-Based Signal-Function FRP System}}
\author{Edward Amsden}
\date{\today}

@@

I intend to show that a monadic evaluation interface and signal vector typing enable a useful and efficient push-based FRP system.

@@

The implementation will be compared against existing pull-based signal function FRP systems.
